---
title: "Global Covid Cases"
output: html_document
---

```{r, include=FALSE}
source("chart1.R")

source("sophia_chart.R")

source("chart2.R")

source("summary_info_script.R")

```

## Introduction 

For our final project, we hope to discover if there is a relationship between the geographic origins of COVID-skeptic tweets and geographic areas with COVID spikes. Without too much difficulty, we were able to find this data which provides actively updated COVID data at the global, continental, and country level.

## Summary of data

To begin our exploration of this data frame, we first calculated the continental location with the highest total deaths in order to get a broad impression of the data. The location with the highest deaths was `r summary_info$highest_death_location`. Then, we wanted to find which country had conducted the most tests. Here, we see that the `r summary_info$highest_test_location` has, by the more recent dates, done the most tests. Additionally, in the data frame there is an interesting variable that rates the strictness of government response to the health crisis on a 0-100 scale. Upon attempting to calculate the country with the highest response stringency, we found that there are 15 countries with a 100 stringency rating `r summary_info$highest_stringency_locations`. Wondering what countries had the lowest stringency score, we found that there are 30 distinct countries with a stringency rating of 0 `r summary_info$lowest_stringency_locations`. Finally, we thought it interesting to find the location where the greatest percentage of the population has been vaccinated. We see that the British territory of `r summary_info$most_percentage_vacc_location` is the location with the highest percentage of the population vaccinated. 


Render your table and describe pertinent observations found in it





**This is a map of the cumulative global Covid-19 cases with the most up to date data.**

```{r, echo = FALSE}
covid_map
```


**Below is a scatterplot comparing the Government Response Stringency Index of each country with their total reported Covid-19 cases per million people in the population.**


```{r, echo = FALSE, message = FALSE}
strin_cases_plot
```

The scatterplot was especially useful in illustrating the relationship between stringency and total cases in each country because of the continuous nature of each variable. The Government Response Stringency Index is a measure based on 9 indicators including school closures, workplace closures, and travel bans. The Index is rescaled to values ranging from 0 to 100, with 100 being the strictest response. It is important to note that each country has multiple data points on the scatterplot to reflect their subsequent change in stringency as the Covid-19 pandemic has unfolded. What's most interesting about this plot is that it reveals how Covid-19 cases seem to rise even as stringency levels increase in countries. This likely reflects a rise in stringency as a response to worsening public health conditions. However, the rate of cases seems to decrease after a stringency index of approximately 63 is enforced. This logically suggests that countries with a high enough stringency index tend experience fewer total Covid-19 cases.


**This is a map showing the relationship between countries death rates and GDP.**
```{r, echo = FALSE}
covid_plot_2
```
This scatterplot shows the overall relationship between countries death rates and GDP. This illuminates the effect resources has on each countries struggle with COVID19. As you can see from the graph, countries with a low amount of GDP struggle significant more than countries with a high amount of GDP. GDP may actualize in terms of increased access to care and housing, increased access to vaccines, and overall better living conditions which have shown to correlate to a lower amount of death (as shown in this graph).
